Visualization of [fulle name] Fractional Integrals

### 2019-03-26 fractional/CMJ style files/article-template.tex
new sentences

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}
%This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.  
\noindent
Fractional-order calculus can be summarized as the generalization of integer-order differentials and integrals to an arbitrary order. It can be argued that 
fractional-order calculus is as old as classical calculus itself. Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$. Leibniz mentiones the notion of a fractional 
order derivative in a letter he sent to L'Hospital. In this letter he answers the following question posed by L'Hospital: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful 
consequences will be drawn}.'' In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional 
integral. It is Liouville and Riemann who laid much of the groundwork which was needed to define what is now known as the Riemann-Liouville fractional integral [Laurent’].

It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
interpretation of the fractional integral. In 1974, this had been the state of affairs for more than 300 years []. Subsequently, the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
geometric interpretations and ecenomic interpretations of the fractional integral.

>>>>

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}
%This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.  
\noindent
Fractional-order calculus can be summarized as the generalization of integer-order differentiation and integration to an arbitrary order. Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$. Leibniz mentiones the notion of a fractional 
order derivative in a letter he sent to L'Hospital. In this letter he answers the following question posed by L'Hospital: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful 
consequences will be drawn}.'' It can, therefore, be argued that fractional-order calculus is as old as classical calculus itself. In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional 
integral. It is Liouville and Riemann who laid much of the groundwork which was needed to define what is now known as the Riemann-Liouville fractional integral [Laurent’].

It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
interpretation of the fractional integral. Interestingly in 1974, this had alreaady been the state of affairs for more than 300 years []. Subsequently, the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
geometric interpretations and ecenomic interpretations of the fractional integral.
